Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2016-01-06 src/tf-cutcell-comparison/responses2.tex
plot and discuss TF advection results

Sections 4a and 4b -- Section 4a presents results for the Sch\"{a}r advection test case for various vertical coordinates and advection schemes; there is little new here that is not already covered in the \citet{schaer2002} paper. The advection tests in section 4b provide an interesting counter example to this test. I would recommend switching the emphasis in these two sections, presenting the advected tracer contours in a new Fig. 3 for the terrain-following advection, and just including results from the Sch\"{a}r case in table 1 for comparison purposes.
\end{quotation}
\TODO{figure 3 will change to show some TF advection results}.  The discussion of the horizontal advection results starting at line \TODO{xxx} has been rewritten more succinctly.

\begin{quotation}
 Lines 131-147 on cut-cell grid generation - It's still not clear how or why a cell vertex  is moved laterally in constructing the cut-cell mesh. Taking Fig. 2 as an example, it  seems that following the authors' directions to move all vertices lying underneath the  orography on the uniform grid up to the surface would produce four grid cells as  shown in the figure below rather than the three cells shown in Fig. 2. This four-cell structure appears to be consistent with the generation of thin cells as the authors  point out in Fig. 5c. If lateral displacement of a vertex is allowed, how is it decided  whether it should be moved and how is it decided where along the surface it should  be located (i.e. the location of point v in Fig. 2)?
\end{quotation}
We have found an alternative method of generating meshes that does not require the use of the \texttt{snappyHexMesh} utility.  This new method does not move vertices laterally and is more straightforward to describe.  This new method creates meshes that retain the long, thin cells from the old method.  The new method is described in section 2 and figure 2.  All test results on cut cell grids have been updated.

>>>>

Sections 4a and 4b -- Section 4a presents results for the Sch\"{a}r advection test case for various vertical coordinates and advection schemes; there is little new here that is not already covered in the \citet{schaer2002} paper. The advection tests in section 4b provide an interesting counter example to this test. I would recommend switching the emphasis in these two sections, presenting the advected tracer contours in a new Fig. 3 for the terrain-following advection, and just including results from the Sch\"{a}r case in table 1 for comparison purposes.
\end{quotation}
Terrain following advection results on BTF and cut cell grids are now shown in figure 3, with the accompanying discussion starting at line \TODO{xxx}.  The analysis of the horizontal advection tests has been rewritten more succinctly and starts at line \TODO{xxx}.

\begin{quotation}
 Lines 131-147 on cut-cell grid generation - It's still not clear how or why a cell vertex  is moved laterally in constructing the cut-cell mesh. Taking Fig. 2 as an example, it  seems that following the authors' directions to move all vertices lying underneath the  orography on the uniform grid up to the surface would produce four grid cells as  shown in the figure below rather than the three cells shown in Fig. 2. This four-cell structure appears to be consistent with the generation of thin cells as the authors  point out in Fig. 5c. If lateral displacement of a vertex is allowed, how is it decided  whether it should be moved and how is it decided where along the surface it should  be located (i.e. the location of point v in Fig. 2)?
\end{quotation}
We have found an alternative method of generating meshes that does not require the use of the \texttt{snappyHexMesh} utility.  This new method does not move vertices laterally and is more straightforward to describe.  This new method creates meshes that retain the long, thin cells from the old method.  The new method is described in section 2 and figure 2.  All test results on cut cell grids have been updated.  \TODO{note changes that have occurred: centred linear scheme no longer unstable in TF advection; larger errors in thermal advection test?}

### 2016-01-06 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
plot and discuss TF advection results

Tracer contours at \(t = \SI{0}{\second}, \SI{5000}{\second}\) and \(\SI{10000}{\second}\) are shown in Figure~\ref{fig:advection-tracer}.
\TODO{discuss figure~\ref{fig:advection-tracer}}
Tracer errors at \(t = \SI{10000}{\second}\) are shown for the \TODO{schemes} in figures \ref{fig:advection-tracer}x and \ref{fig:advection-tracer}x respectively.

@@

\begin{figure*}
	\centering
	\includegraphics{../fig-advection-tracer/fig-advection-tracer.pdf}
%
	\caption{Horizontally advected tracer contours at \(t = \SI{0}{\second}\), \SI{5000}{\second} and \SI{10000}{\second} using (a) centred linear scheme on the BTF grid, (b) the upwind-biased cubic scheme on the cut cell grid, (c) the fourth order scheme from \citet{schaer2002} on the BTF grid, and (d) the upwind-biased cubic scheme on the BTF grid with contour intervals every 0.1.  Errors on the BTF grid at \(t = \SI{10000}{\second}\) are shown for (e) the fourth order scheme from \citet{schaer2002}, and (f) the upwind-biased cubic scheme, with contour intervals every 0.01.  Negative contours denoted by dotted lines.  The terrain profile is also shown immediately above the $x$ axis.  Subfigures (c) and (e) produced using the modified version of the code from \citet{schaer2002}.}
	\label{fig:advection-tracer}
\end{figure*}

>>>>

Tracer contours at \(t = \SI{0}{\second}, \SI{5000}{\second}\) and \(\SI{10000}{\second}\) are shown in Figure~\ref{fig:advection-tracer}.
The most accurate results are found on the BTF grid using the upwind-biased cubic scheme (\ref{fig:advection-tracer}a).  As seen in figure~\ref{fig:advection-tracer}c, errors are less than \num{0.02} in magnitude and are confined to the expected region of the tracer.
At \(t = \SI{5000}{\second}\) the tracer is distorted by the terrain-following velocity field.  On the BTF grid, the tracer correctly returns to its original shape having cleared the mountain by \(t = \SI{10000}{\second}\), but this is not the case with centred linear scheme on the cut cell grid (figure~\ref{fig:advection-tracer}b).  Here, the tracer has spread vertically due to increased numerical errors when the tracer is transported between layers.
Dispersion errors are apparent with grid-scale oscillations that travel in the opposite direction to the wind (figure~\ref{fig:advection-tracer}d) and some artifacts remain above the mountain peak.

Similar accuracy is obtained for both centred linear and upwind-biased cubic schemes on the BTF grid (figures~\ref{fig:advection-tracer}c and~\ref{fig:advection-tracer}e).  However, results are substantially improved by using the upwind-biased cubic scheme on the cut cell grid (figures~\ref{fig:advection-tracer}d and~\ref{fig:advection-tracer}f).
Results on the SLEVE grid are comparable to those on the cut cell grid except that the artifacts above the mountain peak with the centred linear scheme on the cut cell grid are not present on the SLEVE grid (not shown).

@@

\begin{figure*}
	\centering
	\includegraphics{../fig-advection-tracer/fig-advection-tracer.pdf}
%
	\caption{Tracer contours advected in a terrain following velocity field at \(t = \SI{0}{\second}\), \SI{5000}{\second} and \SI{10000}{\second} using (a) the upwind-biased cubic scheme on the BTF grid, and (b) the centred linear scheme on the cut cell grid with contour intervals every 0.1.  Errors at \(t = \SI{10000}{\second}\) are shown for (c) the the upwind-biased cubic scheme on the BTF grid, (d) the centred linear scheme on the cut cell grid, (e) the centred linear scheme on the BTF grid, and (f) the upwind-biased cubic scheme on the cut cell grid with contour intervals every 0.01.  Negative contours denoted by dotted lines.  The terrain profile is also shown immediately above the $x$ axis.}
	\label{fig:advection-tracer}
\end{figure*}
